---
title: "Adrift Summary Dashboard"
format: 
  dashboard:
    orientation: rows
    theme: quartz #see https://bootswatch.com
    # scrolling: true
    logo: /figs/noaa_emblem_logo-2022.png
---
Next Steps: Make a map that can zoom in/out

```{r}
#| label: load-packages
library(here)
library(tidyverse)
library(sf)
library(readr)
```

``` {r}
#| label: load-data
deployDetails <- read_csv(here("output", "deployDetails.csv"))
deployDetails$DeployDuration_days <- round(deployDetails$DeployDuration_days, digits = 1)
deployDetails$RecordDuration_hrs <- round(deployDetails$RecordDuration_hrs, digits = 1)
```

```{r}
#| label: prep-data


```

# Drift

## Row - Value Boxes {height = "30%"}

```{r}
#| label: data-prep

start_date <- as.Date(deployDetails$Deployment_Date[1])
end_date <- as.Date(deployDetails$Recovery_Date[1])
start_end_dates <- paste(start_date, "to", end_date)

start_lat <- deployDetails$Deployment_Latitude[1]
start_lon <- deployDetails$Deployment_Longitude[22]
end_lat <- deployDetails$Recovery_Latitude[22]
end_lon <- deployDetails$Recovery_Longitude[22]

duration <- deployDetails$DeployDuration_days[22] # Duration of deployment/recording

recording <- deployDetails$RecordDuration_hrs[22] # Distance traveled
```

::: {.valuebox icon="calendar3" color="primary"}
Deployment Start/End Dates

`{r} start_date`


:::

::: {.valuebox icon="calendar3" color="primary"}
Retrieval Date

`{r} end_date`


:::

::: {.valuebox icon="calendar-day" color="primary"}
Days of Deployment

`{r} duration`

:::

::: {.valuebox icon="rulers" color="primary"}
Hours of Recording

`{r} recording`

:::

## Row 2 {.tabset}

::: {.card title="Drift Map and Acoustic Scene"}

`{r} view(here("figs", "acoustic_scenes", "ADRIFT_022_AcousticScene.png"))`

```

## Row 2b {.tabset}
```{r}
print("Column 1 in Row 3")

```


# Species
## {.sidebar}

## Row 1 {height = "20%"}
### {width = "40%"}
```{r}
print("Column 1 in Row 1") 
```
### {width = "60%"}
```{r}
print("Column 2 in Row 1")
```
## Row 2 {height = "40%"}
```{r}
print("Column 1 in Row 2")
```
## Row 3 {height = "40%"}
```{r}
print("Column 1 in Row 3")

```