---
title: Dolphins
---
```{r warning=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(here)
source(here::here("R", "_commonR.r"))
source(here::here("R", "reportPlotFunctions.r"))
source(here::here("R", "detTbls", "dolphinTbl.rmd"))

```
::: columns
::: {.column width="40%"}

Dolphins were detected during most Adrift deployments (see table, right), as well as during the combined PASCAL and CCES survey (see table, right, and @fig-AdPC_dolphin_HourlyPresence). While dolphins were detected in all regions during the PASCAL and CCES surveys, they were more frequently detected in the San Francisco and Morro Bay regions during the Adrift study. Dolphin detections included detections that could be positively attributed to Risso's dolphins (Gg) and Pacific white-sided Dolphins (Lo), and detections that remained unidentified (UO) (see table, right). Dolphin acoustic events attributed to Unidentified Odontocetes (UO) were uncommon relative to the number of detections of Risso's and/or Pacific white-sided dolphins.

Dolphin schools in central and northern California are frequently encountered in large, dispersed mixed species groups (S.Rankin, pers. comm.), and here we do not distinguish mixed species from single-species groups. So, attribution of an acoustic event to Risso's dolphins does not preclude the presence of other species. We currently lack a comprehensive acoustic classification routine that includes all dolphin schools in the region. Future research should develop a publicly available acoustic classifier for dolphins that considers mixed species groups and can be applied to different passive acoustic platforms.

:::

::: {.column width="60%"}

```{r dolphinTbl, echo=FALSE, warning=FALSE, message=FALSE}

detTbl

```
:::
:::



Previous research identified different click types for Pacific white-sided dolphins (Soldevilla et al. 2010). The dominant click type in Adrift acoustic encounters of Pacific white-sided dolphins was 'Type A'; however, there were some encounters with 'Type B'. Most of these Type A encounters were at night, similar to Soldevilla et al. (2010), and our research identified a co-occurrence of Click Type A with goose-beaked whale (see Beaked Whales). Future research could investigate this relationship between Pacific white-sided dolphins and goose-beaked whales by taking advantage of the vertical array for separating animals echolocating at the surface and at depth. Soldevilla et al. (2010) suggested Type B echolocation clicks might be attributed to a nearshore population in the southern California Current (Southern California Bight and Baja Mexico); however, our results show that Click Type B can be found in other regions.

Future investigation in the geographic variation in click types for Pacific white-sided dolphins is merited.


![Hourly dolphin events by month, region for Adrift and combined PASCAL, CCES surveys. Hourly presence of dolphins (combined species) (y axis) for different months for combined years (x axis) and for each region (Oregon, Humboldt, San Francisco, and Morro Bay) for Adrift (left) and combined PASCAL and CCES (right). Hourly presence for duty-cycled data relates to the portion of the hour included in the duty cycled data. Black lines represent total available hours (effort) and red lines represent hours with detections. Blue shading represents winter, green represents upwelling, and yellow represents the post-upwelling oceanographic season.](/figs/AdPC_dolphin_HourlyPresence.png){#fig-AdPC_dolphin_HourlyPresence fig-alt="Hourly presence of dolphins detected during the Adrift study (left graph) and the combined PASCAL/CCES surveys (right graph). Detections in Oregon are shown in the top graphs, then Humboldt, San Francisco, and Morro Bay at the bottom. The number of hours is provided on the x-axis, and the date on the y-axis, with seasons shaded in blue for winter, green for upwelling, and yellow for the post-upwelling season. Effort is outlined with a black line, and hours of effort with detections are highlighted in red. Dolphins were detected during most Adrift deployments, though hourly detection varied by drift. Detection of dolphins was lower in the higher latitude (Oregon, Humboldt) deployments for PASCAL and CCES."}


Multiple click types have been described for Risso’s dolphins (Soldevilla et al. 2017). The dominant click type in all acoustic encounters of Risso’s dolphins in our analysis was the “Pelagic Pacific” (PPac) click type. Previous models had limited sample sizes from Risso’s dolphins in open ocean waters, and future investigations should incorporate the acoustic detections from Adrift, PASCAL, and CCES to improve the definition of geographic variation in click types throughout the North Pacific Ocean.

Opportunistic acoustic recordings were collected in the presence of dolphin groups with visually confirmed species, including single and mixed assemblages of Pacific white-sided, North Pacific right whale, Risso’s, and common dolphins. The sample sizes are currently too low to be used to develop classification models, but these recordings will be useful contributions to training datasets in the future.

Detailed methods are provided in our [GitHub online analysis methods](https://sael-swfsc.github.io/adrift-analysis-methods/content/ToothedWhales/Dolphins-Detection.html).
