---
title: "driftDetectionPlots.rmd"
author: "Taiki Sakai"
date: "2024-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plot detections on drift tracks

First load the detection data. Feel free to change the renaming done in `detRename` below,
this is just a starting point from the species codes.

```{r cars}
# this is some common variables and data used for the rest
library(here)
source(here('R/reportPlotFunctions.R'))
gps <- readRDS(here('data/AllDeploymentGPS.rds'))
allDetections <- read.csv(here('data/AllDetections_wGPS.csv'), stringsAsFactors = FALSE)
allDetections$UTC <- as.POSIXct(allDetections$UTC, format='%Y-%m-%d %H:%M:%S', tz='UTC')
allDetections$end <- as.POSIXct(allDetections$end, format='%Y-%m-%d %H:%M:%S', tz='UTC')

detRename <- tribble(
    ~old, ~new,
    'Anthro', 'ship',
    'Mn', 'humpback',
    'Bp', 'fin',
    'Bm', 'blue',
    'B. borealis', 'sei',
    'Lo', 'dolphin',
    'Gg', 'dolphin',
    'UO', 'dolphin',
    'Ba', 'minke',
    'Pm', 'sperm',
    'BB', 'beaked whale',
    'BW', 'beaked whale',
    'BW43', 'beaked whale',
    'ZC', 'beaked whale',
    'MS', 'beaked whale',
    'MC', 'beaked whale',
    'BWC', 'beaked whale',
    'Er', 'gray'
)
for(i in 1:nrow(detRename)) {
    allDetections$species[allDetections$species == detRename$old[i]] <- detRename$new[i]
}
```

### Basic functionality

Tell it what species and drift you want

```{r}
plotTrackDetections(allDetections, gps=gps, plotSpecies = 'humpback', drift='ADRIFT_001')
```

### More than one drift or more than one species (or both!)

plotSpecies and drift can both accept vectors of any number of names

```{r}
plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift='ADRIFT_001')
plotTrackDetections(allDetections, gps=gps, plotSpecies = 'humpback', drift=c('ADRIFT_001', 'ADRIFT_002'))
plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift=c('ADRIFT_001', 'ADRIFT_002'))
```

## Adding titles and changing species legend label

Titles can be added with the title argument, the legend name of the species
can be set with `labs(color=...)`

```{r}
plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift='ADRIFT_001', 
                    title='ADRIFT_001 Whales')
plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift='ADRIFT_001') +
    labs(color='SPECIES')
```

### Changing species colors and/or labels

If plotting multiple species, make sure the order of values/labels matches
the order of breaks, and the names in breaks must match the actual labels in the
data. If only one species you don't need to specify breaks.

```{r}
plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift='ADRIFT_001') +
    scale_color_manual(values=c('red', 'blue'), labels=c('Hump', 'Blue'), breaks=c('humpback', 'blue'))
```

### Saving a PNG

`plotTrackDetections` creates a `ggplot` object, so can be saved to file using `ggsave`, you will
probably need to fiddle with the height/width a bit to get things looking nice. Since it is a map,
the x/y scaling proportion is fixed so the image will not fill the entire space, instead you'll have
extra white area to preserve the map proportions.

```{r}
testPlot <- plotTrackDetections(allDetections, gps=gps, plotSpecies = c('blue', 'humpback'), drift='ADRIFT_001')
ggsave(testPlot, filename=here('figs/sampleTrackDetections.png'), width=6, height=10)
```

