
#Load packages and background data/functions
```{r}
library(here)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source(here::here("R/_commonR.r"))
source(here::here("R/deployDetails.r"))
source(here::here("R/reportPlotFunctions.R"))
```

#Prepare data and make table for Adrift Plots
```{r}
survey <- "ADRIFT" #Choose "ADRIFT" or "CCES" or "PASCAL"

deployDetails_all <- read.csv(here ("output", "deployDetails.csv"))

deployDetails_all$DutyCycle <- if_else(deployDetails_all$RecordingDuration_m != "Continuous",  paste(deployDetails_all$RecordingDuration_m, "min per", deployDetails_all$RecordingInterval_m), "Continuous")

goodCol <- c("Drift_ID", "Site",  "Deployment_Date")

AdriftPlotTable <- deployDetails_all%>%
  filter(Status == "Complete")%>%
  filter(Project == survey) %>%
  rename(Recorder = Type, Drift_ID = Data_ID) %>%
  arrange("Deployment_Date")%>%
  dplyr::select(all_of(goodCol)) 

plotname <- paste(AdriftPlotTable$Drift_ID, "AcousticScene.png", sep = "_")
AdriftPlotTable$AcousticScene <- paste(plotname, "[<https://github.com/shannonrankin/ADRIFT_Report/tree/main/figs/acoustic_scenes/", plotname,  ">]", sep = "")
AdriftPlotTable$DriftPlot <- paste(AdriftPlotTable$Drift_ID, "DriftPlot.png", sep = "_")
AdriftPlotTable$Deployment_Date <- substr(AdriftPlotTable$Deployment_Date, 1, 10)

write.csv(AdriftPlotTable, file = here::here("output/AdriftPlotTable.csv"))
```
#To Do:
# Fix Acoustic Scene so that the link works in the final table output (test table is scratch.qmd)
# Make it so the code does not show up in the final rendered document
#Still need to create the individual drift plots and save to a folder in R
#Learn more by reading R/driftDetectionPlots.rmd

#Once Adrift is finished, then go on to do the same for CCES and PASCAl


#create all driftPlots
```{r}

testPlot <- plotTrackDetections(allDetections, gps=gps, plotSpecies = 'blue', drift='ADRIFT_001')


spp <- c('ship', 'humpback', 'fin', 'blue', 'sei', 'dolphin', 'minke', 'sperm', 'beaked whale', 'gray')
drifts <- AdriftPlotTable$Drift_ID
plotName <- paste(drifts, spp, sep = "-")

#NotWorking, asked Taiki for help 
plotList <- mget(plotTrackDetections(allDetections, gps=gps, plotSpecies = spp, drift=drifts))
invisible(mapply(ggsave, file=paste0(plotName(plotList), "-plot", ".png"), plot=plotList))
  
```
  




  